How do changes in ex vary between countries?

### 2022-03-02 draft_paper.Rmd
add flextable to library and main function to table at bottom. Other refinements still to do.

pacman::p_load(here, tidyverse)

@@

hmd_ex_selected_countries_with_synth %>% 
    filter(year >= 1979) %>% 
    group_by(code, x, sex) %>% 
    arrange(year) %>% 
    mutate(decade = year - (year %% 10)) %>% 
    mutate(delta_ex = ex - lag(ex)) %>%
    nest() %>%
    mutate(
      rwd_model = map(data, ~lm(delta_ex ~ factor(decade), data = . ))
     )  %>%
  mutate(
    tidied_rwd_model = map(rwd_model, broom::tidy)
  ) %>%
  unnest(tidied_rwd_model)
```

>>>>

pacman::p_load(here, tidyverse, flextable) # using flextable instead of gt. It seems to be better 
# developed, more commonly used, and has more clearly labelled function names.

@@

hmd_ex_selected_countries_with_synth %>% 
    filter(year >= 1979) %>% 
    group_by(code, x, sex) %>% 
    arrange(year) %>% 
    mutate(delta_ex = ex - lag(ex)) %>%
    mutate(decade = year - (year %% 10)) %>% 
    filter(!is.na(delta_ex)) %>% 
  group_by(code, x, sex, decade) %>% 
  summarise(
    mean_delta_ex = mean(delta_ex),
    sd_delta_ex   = sd(delta_ex)
    ) %>% 
  ungroup() %>% 
  mutate(cell_contents = glue::glue("{round(mean_delta_ex, 3)} ({round(sd_delta_ex, 3)})")
  ) %>% 
  filter(code == "GBRTENW") %>% 
  filter(x == 0) %>% 
  select(sex, decade, cell_contents) %>% 
  spread(decade, cell_contents) %>% 
  flextable()
